Quantum Hoare Type Theory

### 2020-06-09 ms-paper/ms-paper.tex
Add missing notation for the first bell pair

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {\\}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{->}{{$\rightarrow$}}2 {>=}{{$\geq$}}2 {<-}{{$\leftarrow$}}2
	{<=}{{$\Leftarrow$}}2 {=>}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{>>}{{>>}}2 {>>=}{{>>=}}2
	{|}{{$\vert$}}1 {\\>}{{$\rangle$}}1
	{/\\}{{$\wedge$}}1 {\\/}{{$\vee$}}1
	{\\in}{{$\in$}}1 {\\o}{{$\circ$}}1 {\\Pi}{{$\Pi$}}1
	{|->}{{$\mapsto$}}2 {-o}{{$\multimap$}}2
}

>>>>

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {\\}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{->}{{$\rightarrow$}}2 {>=}{{$\geq$}}2 {<-}{{$\leftarrow$}}2
	{<=}{{$\Leftarrow$}}2 {=>}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{>>}{{>>}}2 {>>=}{{>>=}}2
	{|}{{$\vert$}}1 {\\>}{{$\rangle$}}1
	{/\\}{{$\wedge$}}1 {\\/}{{$\vee$}}1
	{\\in}{{$\in$}}1 {\\o}{{$\circ$}}1 {\\Pi}{{$\Pi$}}1
	{\\Phi+}{{$\Phi^+$}}2
	{|->}{{$\mapsto$}}2 {-o}{{$\multimap$}}2
}
